---
title: "Lab_2 Group_Assigment"
author: "Group_6"
output:
  html_document:
    df_print: paged
---
## Iris dataset

 Iris, introduced by Ronald Fisher in his 1936 paper The use of multiple measurements in taxonomic problems, contains three plant species (setosa, virginica, versicolor) and four features measured for each sample. These quantify the morphologic variation of the iris flower in its three species, all measurements given in centimeters.

### First lets explore datset
```{r}
library("tidyverse")
library("cowplot")
library("GGally")
library("corrplot")
data(iris)
head(iris)
```
```{r}
summary(iris)
```
```{r}
setosa = filter(iris, Species == 'setosa')
versicolor = filter(iris, Species == 'versicolor')
virginica = filter(iris,Species == 'virginica')
summary(setosa)
summary(versicolor)
summary(virginica)
```

### Visualization and Analysis

#### Chart_1
```{r}
ggplot(iris, aes(y = Sepal.Length , x = Sepal.Width)) + geom_point(aes(color = Species), size = 3)
```
#### Analysis/Comments
From the Chart above, we can figure out that distribution of sepal length and width by species, setosa, versicolor, and virginica. According to graph, with the same width, in general, setosa has shorter length, and virginica has longer length. Plus, we can also figure out that sepal width and length has correlation between width and length.

#### Chart_2
```{r}
ggplot(iris, aes(y = Petal.Length , x = Petal.Width)) + geom_point(aes(color = Species), size = 3)
```
#### Analysis/Comments
This graph shows petal width and length by species. As we can see above, it shows same pattern with the above sepal length and width graph. In other words, petal shows correlation between width and length and, in general, virginica has larger width and length than setosa and versicolor.

#### Chart_3 

```{r}
d1 = ggplot( data=iris, aes(x=Sepal.Width, color = Species)) + 
  geom_histogram(fill="skyblue", alpha=0.5,binwidth=0.2) +
  theme_minimal()
d2 = ggplot( data=iris, aes(x=Sepal.Length, color = Species)) + 
  geom_histogram(fill="skyblue", alpha=0.5,binwidth=0.2) +
  theme_minimal()

d3 = ggplot( data=iris, aes(x=Petal.Width, color = Species)) + 
  geom_histogram(fill="skyblue", alpha=0.5,binwidth=0.2) +
  theme_minimal()
d4 = ggplot( data=iris, aes(x=Petal.Length, color = Species)) + 
  geom_histogram(fill="skyblue", alpha=0.5,binwidth=0.2) +
  theme_minimal()
```
```{r}
plot_grid(d1, d2, d3, d4 , 
#          labels = c("A", "B", "C",'D'),
          ncol = 2, nrow = 2)
```
#### Analysis/Comments
We can convert scatter graph to histogram. From the histogram we can see distribution of each species, however, hard to see correlation between width and length. Since each graph has strength and weakness, need to choose proper the graph according to the data type and distribution.

## Overall Chart
```{r}
ggpairs(iris, mapping=ggplot2::aes(colour=Species))
```
#### Analysis/Comments
By Species, setosa, versicolor, and virginica, we can read various distributions.
First, each diagonal positioned graph shows probability density functions. We can estimate distribution. For example, in petal features, we can see setosa has smaller mean and more centralized compare to the other two features.
Second, we can read distribution as well as correlation between each features from second to fourth lines of chart. For example, between sepal length and width, versicolor has strong correlation compare to the otehr factors.
Last, at the fifth line, we can see histogram and box plot and with these info we can see outline of the distribution.

## Mtcars dataset

MTcars data set has data on the design, performance and fuel economy for 32 automobiles from 1973 - 1974. All of the data therein was extracted from the 1974 Motor Trend US magazine.

### First lets explore datset

```{r}
data("mtcars")
head(mtcars)
```

```{r}
summary(mtcars)
```

### Visualization and Analysis
```{r}
mtcars$gear = factor(mtcars$gear,levels=c(3,4,5),
   labels=c("3_Gears","4_Gears","5_Gears"))
```

#### Chart_1 Distribution of Gas Milage
```{r}
qplot(mpg, data=mtcars, geom="density", fill=gear, alpha=I(0.3),
   xlab="Miles Per Gallon",   ylab="Density")
```
#### Analysis/Comments
From the graph above, we can analyze distribution by gears. 5_gear shows higher miles per gallon than 3_gear, however, lower than 4_gear. Plus, although this graph helps to read relation between mean, mode, and skew, it will be more clear if nomarlize the distribution.


#### Chart_2 Mileage by Gear Number
```{r}
qplot(gear, mpg, data=mtcars, geom=c("boxplot"),
   fill=gear,   xlab="", ylab="Miles per Gallon")
```
#### Analysis/Comments
This graph shows quartile distribution. We can see 25%, median, and 75% value more clearly compare to distribution density graph. Moreover, we can understand this data has no outlier. Even box plot shows some calculated values more clearly, it's more convenient to see overall aspect with density distribution graph.


## Correlation
```{r}
data(mtcars)
car_cor=cor(mtcars[,1:11])
round(car_cor,2)
```
#### Analysis/Comments
It shows correlationship between each feature, however, hard to figure out at glance.


## Visualize Correlation
```{r}
corrplot(car_cor)
```
#### Analysis/Comments
It describes exactly same data as above table. By visualizing, however, we can read more easily.
First, the size of the circle means abolute value of the correlation. The bigger the circle, the more correlated. For example, hp has strong correlation with mpg, cyl, and disp, on the other hand, weak correlation with am and gear.
Second, the color shows sign. Blue means positive correlation, while red means negative correlation. For example, hp has strong negative correlation with mpg, however, strong positive correlation with cyl and disp.
